Title Goes Here \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2021-04-13 analysis/paper/shceof.tex
Renderiza todo

\begin{figure}
\centering
\includegraphics{../figures/wave1-o3-1.pdf}
\caption{\label{fig:wave1-o3}Relationship between cEOF1 amplitude and phase with amplitude and phase of the zonal wave 1 in Total Ozone Column averaged between 75°S and 45°S for the period 1979 -- 2019.}
\end{figure}

Indeed, Figure~\ref{fig:wave1-o3} shows the relationship between amplitude and phase of the cEOF1 and the amplitude and phase of the planetary wave 1 in Total Ozone Column between 75°S and 45°S; as shown in Figure~\ref{fig:o3-regr}, this is a wide latitude band that captures most of the area with significant regression coefficients. The correlation between the zonal wave 1 of ozone and cEOF1 (computed as the mean cosine of the difference in phase) is 0.87 (CI: 0.77 -- 0.93). As expected from the location of anomalies in Figure~\ref{fig:wave1-o3}, the Real cEOF1 drives the relationship with amplitude and the Imaginary cEOF1 drives the relationship with phase (not shown).

>>>>

There is a close relationship between amplitude and phase of the cEOF1 and the amplitude and phase of the planetary wave 1 in Total Ozone Column between 75°S and 45°S; as shown in Figure~\ref{fig:o3-regr}, this is a wide latitude band that captures most of the area with significant regression coefficients. The correlation between the amplitude of each index is 0.77 (CI: 0.61 -- 0.87) the overall correlation between the zonal wave 1 of ozone and cEOF1 (computed as the mean cosine of the difference in phase) is 0.87 (CI: 0.77 -- 0.93). As expected from the location of anomalies in Figure~\ref{fig:o3-regr}, the Real cEOF1 drives the relationship with amplitude and the Imaginary cEOF1 drives the relationship with phase (not shown).
